---
title: "Alcohol vs Seat choice"
author: "Eliana Martinez"
date: "Spring 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
boxplot(alcohol~Seat,data=davisdata)
```
  
This boxes overlap. In the boxplot, the median of the back box is higher than that of the front and middle boxes. The front and middle boxes are similar in size, but the middle box has more outliers than the front box. 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The Back Seat likely has more outliers or extreme values that create a wider spread of data. The Front Seat seems to have a much smaller spread, with lower values overall. The Middle Seat represents an intermediate case between the other two, with moderate variability. 

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
There is a one in ten thousand chance of getting these outcomes. To ascertain which sets differ from one another, more investigation is necessary. 

## Conclusions


